A Case Study in Preserving a High Energy Physics Application

### 2014-03-11 paper.tex
add conclusion

>>>>

In this paper, we tries to illustrate the challenges involved in data and software preservation and reproduction through one case study in preserving one High Energy Physics application.
Four different solutions to repeat the original application, together with the pros and cons of each one, are proposed and analyzed. Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction. Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies
